\Huge Conferences in the Era of Expensive Carbon

### 2019-10-15 main.tex
Possible cuts. Some trim.

\bcp{Richard Kim sent a bunch of great comments!  In particular...
  \begin{itemize}
  \item (a) You might say something more about how ACM is in a good position
  to set a trend -- something about taking leadership among scientific
  societies or being on the forefront. There's a little bit about this at
  the end, but it might be developed more into a sentence or paragraph. You
  probably want to phrase this as leadership as opposed to say, sticking
  one's neck out, but there could be something about how computer science and
 tech folks are current and forward-looking, and it's consistent that we
 not be behind the leading edge.
 \item (b) You might say more how ACM needs to prepare itself in light of
 the trends that are coming -- carbon pricing is good organizational sense!
 There's some of this around ACM's potentially needing to adjust its
 business model, but it falls short of making a *business case for carbon
 pricing*, which is what I guess I'm recommending.
 \item Also, in addition to mentioning that Microsoft and other tech
 companies set a price on carbon, you might also note here that Exxon and
 other energy companies set an internal price on carbon as well, as a means
 of risk assessment. In other words, even the oil companies know what's
 coming.
 \end{itemize}
}

@@

Our first proposal is modest: {\bf Every ACM-sponsored conference should
publicly report its carbon footprint}.  Critically, this accounting should include the emissions generated by participants' travel to and from each conference, as this will constitute the bulk of the conference's carbon footprint.
%
Public accounting will nudge conference organizers and attendees to change
their behavior. By analogy, chain restaurants in the US are required by law
to post calorie counts of food items on menu boards, and studies show that
enlightened customers order, on average, up to 50 fewer calories a day as a
result~\cite{menu}.  
%MWH: I don't know why this should be a parenthetical.  Why would the
%analogy be an aside? It is meant to connect the reader's understanding to
%what we are proposing, explciitly; it is meant to be read, not skipped
%over. 
% BCP: In general, parenthetical remarks are not meant to be skipped over:
% they are meant to be read as asides.  I think this reads better in parens,
% but I won't fight for it.

As a case in point, SIGPLAN has been considering how to reduce emissions
over the past couple of years, informed by an accounting of its own
{\COtwoE} expenditures. This discussion has led the organizers of two of its
flagship conferences (POPL and ICFP) to switch from in-person to on-line
program committee meetings (joining a trend among other SIGs, most of which
already use virtual PC meetings for their flagship conferences). This
discussion has also prompted several conferences to increase investments in
livestreaming and video recording to support remote participation.

@@

We acknowledge that carbon offsets are a 
 controversial 
 tool~\cite{anderson2012inconvenient,
 carbon-offsets-are-not-our-get-out-jail-free-card}.  Besides issues with
 verifiability and permanence, some observers worry that---especially at
 their current artificially low cost---they will encourage complacency,
 leading organizations to postpone facing the difficult changes that will
 be required to sustainably decarbonize society.  Offsets
 should be considered as a useful short-term expedient, to be considered in
 parallel with, not instead of, more difficult cutting.
% MWH: It's a bit odd to have two lengthy parenthetical asides in the same
% paragraph. I think this one is on point, so need not be an aside.
% BCP: The whole paragraph was in parens, before.  However, the new paragraph
% header does a decent job of "closing the aside," so I agree the parens can
% go.

@@

ACM should develop tools to gather and publicize this data. As a first step,
SIGPLAN recently built an air-travel-focused {\COtwoE} calculator for
conferences\iflater~\cite{carboncalculator}\bcp{Trim citation?  Is it even
 the right one? Link seems
 dead!  But Richard says ``As a reader, my first question is, how do I get
 access to this calculator? Can you cite this calculator in some way? It
 would be great to give a citation to where people can learn about it or
 use it, even if just, "To learn more about the calculator, e-mail xxx"''}\fi. 
Users can upload conference registration data, and the
calculator will estimate the {\COtwoE} cost of air travel for those
sufficiently far away. This calculator could be expanded to account for
other forms of conference emissions.

>>>>

\bcp{Richard Kim sent a bunch of great comments!  In particular...
  \begin{itemize}
  \item (a) You might say something more about how ACM is in a good position
  to set a trend -- something about taking leadership among scientific
  societies or being on the forefront. There's a little bit about this at
  the end, but it might be developed more into a sentence or paragraph. You
  probably want to phrase this as leadership as opposed to say, sticking
  one's neck out, but there could be something about how computer science \&
  tech folks are current and forward-looking, and it's consistent that we
  not be behind the leading edge.
  \item (b) You might say more how ACM needs to prepare itself in light of
  the trends that are coming -- carbon pricing is good organizational sense!
  There's some of this around ACM's potentially needing to adjust its
  business model, but it falls short of making a *business case for carbon
  pricing*, which is what I guess I'm recommending.
  \item Also, in addition to mentioning that Microsoft and other tech
  companies set a price on carbon, you might also note here that Exxon and
  other energy companies set an internal price on carbon as well, as a means
  of risk assessment. In other words, even the oil companies know what's
  coming.
  \end{itemize}
}

@@

Our first proposal is modest: {\bf Every ACM-sponsored conference should
publicly report its carbon footprint}.  \mwh{CUT: Critically, this accounting should include the emissions generated by participants' travel to and from each conference, as this will constitute the bulk of the conference's carbon footprint.}
%
Public accounting will nudge conference organizers and attendees to change
their behavior. By analogy, chain restaurants in the US are required by law
to post calorie counts of food items on menu boards, and studies show that
enlightened customers order, on average, up to 50 fewer calories a day as a
result~\cite{menu}.  
%MWH: I don't know why this should be a parenthetical.  Why would the
%analogy be an aside? It is meant to connect the reader's understanding to
%what we are proposing, explciitly; it is meant to be read, not skipped
%over. 
% BCP: In general, parenthetical remarks are not meant to be skipped over:
% they are meant to be read as asides.  I think this reads better in parens,
% but I won't fight for it.

As a case in point, SIGPLAN has been considering how to reduce emissions
over the past couple of years, informed by an accounting of its own
{\COtwoE} expenditures. This discussion has led the organizers of two of its
flagship conferences (POPL and ICFP) to switch from in-person to on-line
program committee meetings (joining a trend among other SIGs). This
discussion has also prompted several conferences to increase investments in
livestreaming and video recording to support remote participation.

@@

We acknowledge that carbon offsets are a 
  controversial 
  tool~\cite{anderson2012inconvenient,
  carbon-offsets-are-not-our-get-out-jail-free-card}.  \mwh{CUT: Besides issues with
  verifiability and permanence, some observers worry that---especially at
  their current artificially low cost---they will encourage complacency,
  leading organizations to postpone facing the difficult changes that will
  be required to sustainably decarbonize society.} Offsets are a
useful short-term expedient, not a replacement for more difficult
cutting. 
% MWH: It's a bit odd to have two lengthy parenthetical asides in the same
% paragraph. I think this one is on point, so need not be an aside.
% BCP: The whole paragraph was in parens, before.  However, the new paragraph
% header does a decent job of "closing the aside," so I agree the parens can
% go.

@@

ACM should develop tools to gather and publicize this data. As a first step,
SIGPLAN recently built an air-travel-focused {\COtwoE} calculator for
conferences\iflater~\cite{carboncalculator}\bcp{Trim citation?  Is it even
  the right one? Link seems
  dead!  But Richard says ``As a reader, my first question is, how do I get
  access to this calculator? Can you cite this calculator in some way? It
  would be great to give a citation to where people can learn about it or
  use it, even if just, "To learn more about the calculator, e-mail
  \_\_\_\_\_\_\_\_\_."''}\fi. Users can upload conference registration data, and the
calculator will estimate the {\COtwoE} cost of air travel for those
sufficiently far away. This calculator could be expanded to account for
other forms of conference emissions.
